The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
More rewording of the paper.

There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FrobeniusThresholds}.
\begin{itemize}
\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ described above.
\item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
\item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}.
\end{itemize}
This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.

@@

This calls the function {\tt isSimpleNormalCrossing} which is also exposed to the user.  Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).

@@

\section{Future work}

>>>>

There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FrobeniusThresholds}.
\begin{itemize}
\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ described above.
\item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
\item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}.
\end{itemize}

This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.

@@

To verify whether $f$ factors into simple normal crossing factors, the function {\tt isSimpleNormalCrossing} is called.  This function is also exposed to the user.  Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).

@@

\newpage
\section{Future work}

We conclude this note with some comments on possible future improvements to the package.
